Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-24 analysis/paper/paper.Rmd
Adds Eckert2020 reference

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.

<!--# These references above are all prior 2017. We may want to update the list? I've added two using insert citation tool of the visual editor rmarkdown -->

>>>>

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research was recently highlighted by many authors [@Tiwari_2021; @Eckert2020; @preeyanon2018; @Wallach2018; @Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
